Methods Power Study

### 2022-09-12 simulation_study/simulate_summary.Rmd
data updates

```{r simulation_pipeline, include = T, echo = T}
# a list to save this in 
full_simulation <- list()
populations <- simulate_population(x)

@@

```{r}
sim_mac <- readRDS("simulation_2022-08-14 12:54:44.Rdata")
sim_win
sim_linux

all_sim <- bind_rows(sim_mac, .id = "id")

summary_long <- all_sim %>% 
  group_by(scale, original_n, source, name, power) %>% 
  summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")
```

@@

```{r}

>>>>

```{r simulation_pipeline, include = T, echo = T, eval = F}
# a list to save this in 
full_simulation <- list()
populations <- simulate_population(x)

@@

```{r eval = F}
all_sim <- bind_rows(
  bind_rows(readRDS("simulation_linux4_0815.Rdata")), 
  bind_rows(readRDS("simulation_linux8_0815.Rdata")), 
  bind_rows(readRDS("simulation_linux8_0816.Rdata")),
  bind_rows(readRDS("simulation_linux36_0819.Rdata")),
  bind_rows(readRDS("simulation_windows3_0815.Rdata")), 
  bind_rows(readRDS("simulation_windows39_0819.Rdata")),
  bind_rows(readRDS("simulation_mac_0815.Rdata")), 
  bind_rows(readRDS("simulation_mac_0817.Rdata"))
) %>% unique()

summary_long <- all_sim %>% 
  group_by(scale, original_n, source, name, power, scale2) %>% 
  summarize(
    n = n(),
    sample_size = mean(sample_size),
    value = mean(value), 
    sd_item = mean(sd_item),
    .groups = "keep")

@@

```{r}
export(summary_long, "simulated_summary_data_update.csv", row.names = F)
```
